FinalManuscript_DISCS_UG

### 2018-06-25 parts/01_introduction_03objectives.tex
Finished chapter 2 + other fixes

A paper published in 2009 by Ziad, et. al. presents \textit{CryptoImg}, a library for the  Open Source Computer Vision Library (OpenCV) \cite{opencv_library} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem \cite{ziad_cryptoimg:_2016}. While \textit{CryptoImg} demonstrates that various image manipulation operations are possible in a homomorphic system, we believe this study can be extended by considering other known homomorphic encryption schemes, such as an elliptic curve and ElGamal based cryptosystem presented by Li, et. al. \cite{li_elliptic_2012}, and the fully homomorphic encryption scheme proposed by Smart and Vercauteren \cite{hutchison_fully_2010}. Our study aims to provide an objective comparision of various homomorphic cryptosystems currently in the literature, as they would be used in encrypted image manipulation.
Furthermore, one of the main problems in homomorphic encryption is the practicality of homomorphic encryption schemes. Homomorphic cryptosystems are known to be slower compared to other cryptosystems \cite{sen_homomorphic_2013}.
Taking the above into account, in this study, we wish to
\begin{enumerate}
    \item Compare the applicability of known homomorphic encryption schemes to common image processsing operations, in other words, determine which schemes permit more image processing operations;
		\item Compare the security of common image processing operations under known homomorphic encryption schemes, using established statistical methods in image encryption;
    \item Compare the efficiency of common image processsing operations under known homomorphic encryption schemes;
    \item Create a library for OpenCV to allow for convenient use and comparison of these homomorphic encryption schemes.
\end{enumerate}

>>>>

A paper published in 2009 by Ziad, et. al. presents \textit{CryptoImg}, a library for the  Open Source Computer Vision Library (OpenCV) \cite{bradski_opencv_2000} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem \cite{ziad_cryptoimg:_2016}. While \textit{CryptoImg} demonstrates that various image manipulation operations are possible in a homomorphic system, we believe this study can be extended by considering other known homomorphic encryption schemes, such as an elliptic curve and ElGamal based cryptosystem presented by Li, et. al. \cite{li_elliptic_2012}, and the fully homomorphic encryption scheme proposed by Smart and Vercauteren \cite{hutchison_fully_2010}. Our study aims to provide an objective comparision of various homomorphic cryptosystems currently in the literature, as they would be used in encrypted image manipulation.
Furthermore, one of the main problems in homomorphic encryption is the practicality of homomorphic encryption schemes. Homomorphic cryptosystems are known to be slower compared to other cryptosystems \cite{sen_homomorphic_2013}.
Taking the above into account, in this study, we wish to
\begin{enumerate}
    \item Compare the applicability of known homomorphic encryption schemes to common image processsing operations, in other words, determine which schemes permit more image processing operations;
		\item Compare the security of common image processing operations under known homomorphic encryption schemes, using established statistical methods in image encryption;
    \item Compare the efficiency of common image processsing operations under known homomorphic encryption schemes;
    \item Create a library for OpenCV to allow for convenient use and comparison of these homomorphic encryption schemes.
\end{enumerate}

### 2018-06-25 parts/02_relatedliterature.tex
Finished chapter 2 + other fixes

\section{An Introduction to Cryptography and Cryptosystems}
% [include mention of metrics by which they are compared]

In cryptography, a cryptosystem consists of an encryption function $\mathcal{E}$ and a decryption function $\mathcal{D}$, along with the plaintext space $\mathcal{P}$, ciphertext space $\mathcal{C}$ and the key space $\mathcal{K}$~\cite{tilborg_encyclopedia_2005}. A \textit{plaintext} is text that can be easily understood by everybody. On the other hand, a \textit{ciphertext} is a result from encrypting the plaintext using an encryption key. The plaintext space consists of all the possible plaintexts.

There are two kinds of cryptosystems, namely: \textit{symmetric} and \textit{asymmetric}. In symmetric encryption, the key is used for both encryption and decryption. On the other hand, asymmetric cryptosystems use separate keys for encryption and decryption. The encryption key (also called the \textit{public key}) is shared to everybody, while the decryption key (also called the \textit{private key}) is kept secret. Because of this, there is no need to agree upon some secure key sharing protocols. Usually, the security of asymmetric cryptosystems relies on the intractability of certain computational problems, like the RSA depends on the difficulty of integer factorization, while ElGamal depends on the difficulty of the discrete logarithmic problem.

A cryptosystem is said to be homomorphic if its encryption function is homomorphic, that is, if it satisfies the relation
\begin{equation}
    \mathcal{E}\left(p_1 \otimes p_2\right) = \mathcal{E}\left(p_1\right) \oplus \mathcal{E}\left(p_2\right)
\end{equation}
where $\otimes$ and $\oplus$ are operations in $\mathcal{P}$ and $\mathcal{C}$ respectively \cite{fontaine_survey_2007}.

@@

% we may refer to the classification in the CryptoImg paper

@@

\subsection{Edge Detection and Spatial Filters}
Edge detection is used to find and determine the boundaries in an image, commonly used in applications such as image segmentation and feature extraction. This works by detecting so-called \textit{edges}, areas that have abrupt changes in intensity. 
Edge detection is usually done by using gradient operators that detect such abrupt changes. These operators are commonly known as \textit{spatial filter}, which are usually of $3 \times 3$ size. A common example of spatial filters is the Sobel operator, with two matrices (also called as kernels) $g_x$ and $g_y$ representing the horizontal and vertical components respectively.
\begin{equation}
    g_x = 
    \begin{bmatrix}
        -1 & 0 & 1 \\
        -2 & 0 & 2 \\
        -1 & 0 & 1
    \end{bmatrix}
    \qquad\text{and}\qquad
    g_y = 
    \begin{bmatrix}
        1 & 2 & 1 \\
        0 & 0 & 0 \\
        -1 & -2 & -1
    \end{bmatrix}
\end{equation}

To get the resulting image $I^\prime$, a convolution is performed between the original image $I$ of size $M \times N$ and the kernel $k$ of size $m \times n$. Now suppose that the pixel value of an image at point $\left(i,j\right)$ is $r_{i,j}$. Then, a transformation using spatial filters can be described as follows:
\begin{align}
    T\left(r_{i,j}\right) &= \left[k * I\right]\left(\left\lfloor\frac{m}{2}\right\rfloor, \left\lfloor\frac{n}{2}\right\rfloor \right) \\
                         &= \sum_{u=1}^{m} \sum_{v=1}^{n} \left[k_{i,j} r_{i+u, j+v} \right]
\end{align}

Spatial filters are not only used for edge detection, but there are filters that do image blurring (such as Gaussian blur and box blur) and image sharpening.
% Should I put a table of other kernels too?

\section{Related Work and Previous Implementations}
There has been work done regarding the implementation of 
CryptoImg

example of homomorphic encryption / image manipulation past work

minor limitation: improvement on previous work, but not a direct comparison

major limitation: does not discuss security: are modified images also secure?

HElib

\section{Summary}

>>>>

\section{Homomorphic Cryptosystems}
% [include mention of metrics by which they are compared]

In cryptography, a cryptosystem consists of an encryption function $\mathcal{E}$ and a decryption function $\mathcal{D}$, along with the plaintext space $\mathcal{P}$, ciphertext space $\mathcal{C}$ and the key space $\mathcal{K}$~\cite{bauer_cryptosystem_2005}. A \textit{plaintext} is text that can be easily understood by everybody. On the other hand, a \textit{ciphertext} is a result from encrypting the plaintext using an encryption key. The \textit{plaintext space} is the set of all possible plaintexts, the \textit{ciphertext space} is the set of all possible ciphertexts, while the \textit{keyspace} consists of all possible keys.

There are two kinds of cryptosystems, namely: \textit{symmetric} and \textit{asymmetric}. In symmetric-key cryptosystems, the same key is used for both encryption and decryption. As a consequence, the encryption and decryption functions are inverses of each other. Prominent examples of symmetric-key cryptosystems are the Data Encryption Standard (DES), and its replacement, the Advanced Encryption Standard (AES).

On the other hand, asymmetric-key (or public-key) cryptosystems use separate keys for encryption and decryption. The encryption key (also called the \textit{public key}) is shared to everybody, while the decryption key (also called the \textit{private key}) is kept secret. Because of this, there is no need to agree upon some secure key sharing protocols. Usually, the security of asymmetric-key cryptosystems relies on the intractability of certain computational problems, like how RSA depends on the difficulty of integer factorization \cite{rivest_method_1978}, while ElGamal depends on the difficulty of the discrete logarithm problem \cite{blakley_public_1985}.

A cryptosystem is said to be homomorphic if its encryption function is homomorphic, that is, if it satisfies the relation
\begin{equation}
    \mathcal{E}_k \left(p_1 \boxplus p_2\right) = \mathcal{E}_k \left(p_1\right) \oplus \mathcal{E}_k \left(p_2\right)
\end{equation}
where $p_1, p_2 \in \mathcal{P}$ are the plaintexts, $k \in \mathcal{K}$ is the encryption key, and $\boxplus$ and $\oplus$ are operations in $\mathcal{P}$ and $\mathcal{C}$ respectively \cite{fontaine_survey_2007}. Furthermore, suppose in a public-key cryptosystem, let $\mathcal{E}_k \left(p \right)$ be the encryption function using the public key $k$, and $\mathcal{D}_l \left(c \right)$ be the decryption function using the private key $l$. Then this cryptosystem is homomorphic if it satisfies
\begin{equation}
    p_1 \boxplus p_2 = \mathcal{D}_l \left( \mathcal{E}_k \left(p_1\right) \oplus \mathcal{E}_k \left(p_2\right) \right)
\end{equation}
where $p_1, p_2 \in \mathcal{P}$ are the plaintexts \cite{li_elliptic_2012}.
In other words, a homomorphic cryptosystem preserves the operations that can be typically done with the plaintext without the intermediary step of decrypting the ciphertext beforehand.

Some examples of homomorphic cryptosystems include the Goldwasser-Micali cryptosystem \cite{goldwasser_probabilistic_1984} and the Paillier cryptosystem \cite{stern_public-key_1999}. Even the classic public-key cryptosystems are homomorphic, both RSA and ElGamal are multiplicatively homomorphic, while elliptic curve cryptosystems are additively homomorphic \cite{li_elliptic_2012}.

However, there exists a \textit{fully homomorphic} cryptosystem, where instead of being limited to operations like addition or multiplication, it allows any arbitrary operations on the ciphertext. It is only in recent years that a fully homomorphic cryptosystem has been described. Gentry's cryptosystem, which uses lattice-based cryptography, allows arbitrary functions that are constructed from various addition and multiplication operations \cite{gentry_fully_2009}.

A recent survey of homomorphic encryption by Sen shows that the open problems in the area deal with fully homomorphic encryption, of which the main concern is the speed of such implementations \cite{sen_homomorphic_2013}.

@@

% we may refer to the classification in the CryptoImg paper
Knowing that most of the common image operations rely on addition and multiplication operations, adopting a fully homomorphic cryptosystem enables image processing operations on encrypted images without the need of decryption.

@@

\subsection{Edge Detection and Spatial Filtering}
Edge detection is used to find and determine the boundaries in an image, commonly used in applications such as image segmentation and feature extraction. This works by detecting so-called \textit{edges}, areas that have abrupt changes in intensity.

Edge detection is usually done by using gradient operators that detect such abrupt changes. These operators are commonly known as \textit{spatial filter}, which are usually of $3 \times 3$ size. A common example of spatial filters is the Sobel operator, with two matrices (also called as kernels) $g_x$ and $g_y$ representing the horizontal and vertical components respectively.
\begin{equation}
    g_x = 
    \begin{bmatrix}
        -1 & 0 & 1 \\
        -2 & 0 & 2 \\
        -1 & 0 & 1
    \end{bmatrix}
    \qquad\text{and}\qquad
    g_y = 
    \begin{bmatrix}
        1 & 2 & 1 \\
        0 & 0 & 0 \\
        -1 & -2 & -1
    \end{bmatrix}
\end{equation}
To get the resulting image $I^\prime$, a convolution is performed between the original image $I$ of size $M \times N$ and the kernel $k$ of size $m \times n$. Now suppose that the pixel value of an image at point $\left(i,j\right)$ is $r_{i,j}$. Then, a transformation using spatial filters can be described as follows:
\begin{align}
    T\left(r_{i,j}\right) &= \left[k * I\right]\left(\left\lfloor\frac{m}{2}\right\rfloor, \left\lfloor\frac{n}{2}\right\rfloor \right) \\
                         &= \sum_{u=1}^{m} \sum_{v=1}^{n} \left[k_{i,j} r_{i+u, j+v} \right]
\end{align}

Spatial filters are not only used for edge detection, but there are also filters that do image smoothing (such as Gaussian blur and box blur, $b_g$ and $b$ respectively in Equation~\ref{eqn:smooth-filters}) and image sharpening, to name a few \cite{gonzalez_digital_2008}.
\begin{equation}
    \label{eqn:smooth-filters}
    b_g = \frac{1}{16}
    \begin{bmatrix}
        1 & 2 & 1 \\
        2 & 4 & 2 \\
        1 & 2 & 1
    \end{bmatrix}
    \qquad
    b = \frac{1}{9}
    \begin{bmatrix}
        1 & 1 & 1 \\
        1 & 1 & 1 \\
        1 & 1 & 1
    \end{bmatrix}
\end{equation}
% Should I put a table of other kernels too?

\section{Related Work and Previous Implementations}
% CryptoImg

% example of homomorphic encryption / image manipulation past work

% minor limitation: improvement on previous work, but not a direct comparison

% major limitation: does not discuss security: are modified images also secure?

There has been work done regarding the application of homomorphic cryptosystems in image processing. In particular, Ziad, et al. introduced a library called \textit{CryptoImg} that uses the homomorphic properties of the Paillier cryptosystem to apply image operations securely \cite{ziad_cryptoimg:_2016}. This shows that it is indeed possible to do various image operations in a homomorphic cryptosystem.

However, a major limitation of \textit{CryptoImg} is that it does not seem to tackle the problem of security. Even though the authors claim that the operations in \textit{CryptoImg} are privacy-preserving, it is not clear whether the modified images are secure as well.
This study can be further improved by also considering the use of other homomorphic cryptosystems like the elliptic curve-based ElGamal cryptosystem by Li, et al. \cite{li_elliptic_2012} and a fully homomorphic cryptosystem introduced by Smart and Vercauteren \cite{hutchison_fully_2010}, which is a variant of Gentry's lattice-based cryptosystem.

% HElib
Another related work would be the implementation of a fully homomorphic encryption. Halevi and Shoup \cite{garay_algorithms_2014} introduced \textit{HElib}, a library that implements the Brakerski-Gentry-Vaikuntanathan (BGV) homomorphic cryptosystem. This library also makes use of various optimizations to speed up the homomorphic operations, due to homomorphic cryptosystems being slower than other cryptosystems \cite{sen_homomorphic_2013}.

\section{Summary}
We have seen how various image processing operations make use of a series of additions and multiplications. Because of this, it is possible to use a homomorphic cryptosystem in order to apply image operations directly on encrypted images, as demonstrated by the \textit{CryptoImg} library.

In particular, we aim to address the shortcoming of \textit{CryptoImg} by developing a library to test various homomorphic encryption schemes with the help of the \textit{HElib} library to be able to implement fully homomorphic encryption schemes. This helps us determine the practicality of using homomorphic cryptosystems in image processing, especially when dealing with more complex image operations.

### 2018-06-25 parts/03_methodology.tex
Finished chapter 2 + other fixes

The current version of the OpenCV library (3.4.1) will be forked from the open-source GitHub repository at https://github.com/opencv \cite{opencv_library}.

@@

Aside from implementing the homomorphic encryption and decryption algorithms, we will also implement library functions for the following image processing functions, as they are defined in \cite{gonzalez_digital_2008}. We will also take note of whether or not a candidate operation is impossible to perform under a given cryptosystem.  We let $R(x,y)$ denote the intensity at coordinate $(x,y)$ in the source image, and $S(x,y)$ denote the intensity at coordinate $(x,y)$ in the resulting image. We further suppose that the intensity values of pixels are in the range $[0, L-1]$.
\begin{description}
	\item[Intensity transformations.] Transformations on the intensities of each of the pixels on an image. The following definitions hold for all $x,y$.
	\begin{enumerate}
		\item Image negation: $S(x,y) = L - 1 - R(x,y)$.
		\item Log transformation: $S(x,y) = c\log{(1 + R(x,y))}$, $c \geq 0$.
		\item Power-law transformation: $S(x,y) = c[R(x,y)]^\gamma$, $c > 0, \gamma > 0$.
	\end{enumerate}
	\item[Spatial filters.] Filters implemented by performing a convolution between an $M\times N$ source image and an $m\times n$ filter matrix. Let $W$ be a filter matrix. Then the corresponding spatial filter is given by
	\begin{align}
		S(x,y) = \sum_{s=1}^m{\sum_{t=1}^n{W(s,t)R(x+s,y+t)}}.
	\end{align}
	\item [Histogram processing / equalization]

\end{description}

@@

For each plaintext image (PT), we will consider each image operation listed above and generate three images: a plaintext domain transformation (PDT), a ciphertext image (CT), and an encrypted domain transformation (EDT). The cipherThe PDT will be generated by running the image operation on the original image. The CT will be generated by encrypting the image, then applying the operation, and the EDT will be generated by decrypting the CT. The four images (PT, PDT, CT, CDT) will then be compared using various benchmarks to evaluate the quality and security of each homomorphic encryption scheme.

@@

\subsection{Evaluating Image Quality}
The benchmarks to be used in the study, adopted from \cite{ahmed_benchmark_2016, ahmad_efficiency_2012, wu_npcr_2011} are listed below. We let $X_i$ denote a value in an image $X$, where $1 \leq i \leq N$.
We first perform three tests to ascertain the preservation of image quality after encryption and decryption: MSE, PSNR, and SSIM.
\begin{description}
	\item [Mean Squared Error (MSE).] The MSE is defined in \cite{ahmed_benchmark_2016} as
	\begin{align}
		MSE = \frac{1}{N}\sum_{i=1}^{N}{(CDT_i - PDT_i)^2}.
	\end{align}
	The MSE provides a measure of how much data is recovered if an image operation is applied on the encrypted image, which is then decrypted. Lower values of MSE indicate higher preservation of image quality \cite{ahmed_benchmark_2016, ahmad_efficiency_2012}.
	\item [Peak Signal to Noise Ratio (PSNR).]
	According to Ahmed, et al. \cite{ahmed_benchmark_2016}, PSNR is ``an estimator for human visual perception of reconstruction quality'' which is based on  It has been used to ascertain image quality in various studies and is a known meetric for image and video quality \cite{upmanyu_efficient_2009, jain_image_2016, akramullah_video_2014}. Although it may produce results which do not correlate with human visual perception \cite{huynh-thu_accuracy_2012, ahmed_benchmark_2016}, it is a valid indicator of image quality when media containing the same visual content is compared \cite{huynh-thu_accuracy_2012}.
	PSNR is defined by
	\begin{align}
		PSNR = 10\log_{10}{\left( \frac{L^2}{MSE} \right)}
	\end{align}
	where $L$ is the maximum pixel intensity value of an image.
	Despite the known limitations of PSNR, since we are going to compare the effect of each encryption scheme on recovered image quality, given a fixed library of images, it is a valid measure of image quality for the study. A higher PSNR indicates higher image quality preservation.
	\item [Structural Similarity Index (SSIM).]
	The SSIM for two random variables $X$ and $Y$ is defined in \cite{ahmed_benchmark_2016, akramullah_video_2014} as
	\begin{align}
		SSIM(X,Y) = \frac{(2\mu_X\mu_Y+c_1)(2\sigma_{XY}+c_2)}{(\mu_X^2+\mu_Y^2+c_1)(\mu_X^2+\mu_Y^2+c_2)}
	\end{align}
	where
	\begin{itemize}
		\item $\mu_X, \mu_Y$ are the averages of $X$ and $Y$, respectively;
		\item $\sigma_X, \sigma_Y$ are the variances of $X$ and $Y$, respectively;
		\item $\sigma_{XY}$ is the covariance of $X$ and $Y$;
		\item $c_1 = (k_1L)^2, c_2 = (k_2L)^2$ are two variables used to stabilize the measure when $\mu_X^2+\mu_Y^2$ is close to zero \cite{akramullah_video_2014};
		\item $L$ is the the maximum pixel intensity value of an image;
		\item $k_1 = 0.01, k_2 = 0.03$ by default, given in \cite{ahmed_benchmark_2016}.
	\end{itemize}
	The SSIM is applied to the luminance value of two images to gauge structural similarity between neighboring pixels.
	For the study, we will compute $SSIM(PDT, CDT)$ for every image operation, under each homomorphic cryptosystem. Higher values of SSIM indicate higher structural similarity, and an SSIM of 1 indicates that the two images are identical\cite{ahmed_benchmark_2016}.
\end{description}

@@

	We will compute $H(CDT)$ for every image operation, under each homomorphic cryptosystem, and compare the effects of each image operation on the entropy of the encrypted image. Ideally, performing image operations on encrypted images should still maintain a high level of entropy.
	\item [Correlation coefficient analysis (CC).]
		Images generally have a high degree of similarity between adjacent pixels. This correlation must be hidden in the encrypted image, even after performing image operations.
		The correlation coefficient of an image can be computed between adjacent pixels either vertically, horizontal, or diagonally, and is defined in \cite{ahmed_benchmark_2016} by:
		\begin{align}
			CC(X,Y) = \frac{\sigma_{X,Y}}{\sqrt{\sigma_X}\times\sqrt{\sigma_Y}}
		\end{align}
		where
		\begin{itemize}
			\item $\sigma_X, \sigma_Y$ are the variances of $X$ and $Y$, respectively;
			\item $\sigma_{XY}$ is the covariance of $X$ and $Y$.
		\end{itemize}

		For every $CDT$ image, we will compute for the correlation coefficient (for vertical, horizontal and diagonal correlation) for every image operation, under each homomorphic cryptosystem.
	\item [NPCR and UACI.]
		The Number of Pixel Change Rate (NPCR) measures the number of pixels which are changed between the a plaintext and a ciphertext to quantify the amount of dispersion which occurs during encryption.

@@

		The NPCR and UACI between two images $X$ and $Y$, each containing $N$ pixels indexed from $1$ to $N$ is defined in \cite{wu_npcr_2011} as
		\begin{align}
			NPCR(X,Y) &= \frac{1}{N}\sum_{i = 1}^{N}{D(X_i,Y_i)} \times 100\%\\
			UACI(X,Y) &= \frac{1}{L_{max} \times N} \sum_{i = 1}^{N}{ |L(X_i) - L(Y_i)| } \times 100\%
		\end{align}
		where
		\begin{itemize}
			\item $X_i$ and $Y_i$ are the $i$th pixels of $X$ and $Y$, respectively;
			\item $D$ is a difference function between pixels $A$ and $B$ defined by
			\begin{align}
				D(A,B) =
				\begin{cases}
					0 &  \text{if $A = B$},\\
					1 &  \text{if $A \neq B$};
				\end{cases}
			\end{align}
		\item $L_{max}$ is the maximum intensity of a pixel;
		\item $L(X_i)$ and $L(Y_i)$ are the intensities of pixels $X_i$ and $Y_i$, respectively.
		\end{itemize}
		We will calculate $NPCR(PDT,CDT)$ and $UACI(PDT,CDT)$  for every image operation, under each homomorphic cryptosystem. A high NPCR and UACI are desired to ensure high dispersion and security against differential attacks \cite{ahmed_benchmark_2016}. Critical values for NPCR and UACI for given image sizes and bit depths are given in  \cite{wu_npcr_2011}.
\end{description}

>>>>

The current version of the OpenCV library (3.4.1) will be forked from the open-source GitHub repository at \url{https://github.com/opencv/opencv} \cite{bradski_opencv_2000}.

@@

Aside from implementing the homomorphic encryption and decryption algorithms, we will also implement library functions for the following image processing functions, as they are defined in \cite{gonzalez_digital_2008}. We will also take note of whether or not a candidate operation is impossible to perform under a given cryptosystem.  We let $R(x,y)$ denote the intensity at coordinate $(x,y)$ in the source image, and $S(x,y)$ denote the intensity at coordinate $(x,y)$ in the resulting image. We further suppose that the intensity values of pixels are in the range $[0, L-1]$.
\begin{description}
	\item[Intensity transformations.] Transformations on the intensities of each of the pixels on an image. The following definitions hold for all $x,y$.
	\begin{enumerate}
		\item Image negation: $S(x,y) = L - 1 - R(x,y)$.
		\item Log transformation: $S(x,y) = c\log{(1 + R(x,y))}$, $c \geq 0$.
		\item Power-law transformation: $S(x,y) = c[R(x,y)]^\gamma$, $c > 0, \gamma > 0$.
	\end{enumerate}
	\item[Spatial filters.] Filters implemented by performing a convolution between an $M\times N$ source image and an $m\times n$ filter matrix. Let $W$ be a filter matrix. Then the corresponding spatial filter is given by
	\begin{align}
		S(x,y) = \sum_{s=1}^m{\sum_{t=1}^n{W(s,t)R(x+s,y+t)}}.
	\end{align}
	Morphological operations such as erosion and dilation can be achieved using convolution as well.
\end{description}

@@

For each plaintext image (PT), we will consider each image operation listed above and generate three images: a plaintext domain transformation (PDT), a ciphertext image (CT), and an encrypted domain transformation (EDT). The PDT will be generated by running the image operation on the original image. The CT will be generated by encrypting the image, then applying the operation, and the EDT will be generated by decrypting the CT. The four images (PT, PDT, CT, CDT) will then be compared using various benchmarks to evaluate the quality and security of each homomorphic encryption scheme.

@@

\subsection{Evaluating Image Quality}
The benchmarks to be used in the study, adopted from \cite{ahmed_benchmark_2016, ahmad_efficiency_2012, wu_npcr_2011} are listed below. We let $X_i$ denote a value in an image $X$, where $1 \leq i \leq N$.
We first perform three tests to ascertain the preservation of image quality after encryption and decryption: MSE, PSNR, and SSIM.
\begin{description}
	\item [Mean Squared Error (MSE).] The MSE is defined in \cite{ahmed_benchmark_2016} as
	\begin{align}
		\mathrm{MSE} = \frac{1}{N}\sum_{i=1}^{N}{(\mathrm{CDT}_i - \mathrm{PDT}_i)^2}.
	\end{align}
	The MSE provides a measure of how much data is recovered if an image operation is applied on the encrypted image, which is then decrypted. Lower values of MSE indicate higher preservation of image quality \cite{ahmed_benchmark_2016, ahmad_efficiency_2012}.
	\item [Peak Signal to Noise Ratio (PSNR).]
	According to Ahmed, et al. \cite{ahmed_benchmark_2016}, PSNR is ``an estimator for human visual perception of reconstruction quality'' which is based on  It has been used to ascertain image quality in various studies and is a known metric for image and video quality \cite{upmanyu_efficient_2009, jain_image_2016, akramullah_video_2014}. Although it may produce results which do not correlate with human visual perception \cite{huynh-thu_accuracy_2012, ahmed_benchmark_2016}, it is a valid indicator of image quality when media containing the same visual content is compared \cite{huynh-thu_accuracy_2012}.
	PSNR is defined by
	\begin{align}
		\mathrm{PSNR} = 10\log_{10}{\left( \frac{L^2}{\mathrm{MSE}} \right)}
	\end{align}
	where $L$ is the maximum pixel intensity value of an image.
	Despite the known limitations of PSNR, since we are going to compare the effect of each encryption scheme on recovered image quality, given a fixed library of images, it is a valid measure of image quality for the study. A higher PSNR indicates higher image quality preservation.
	\item [Structural Similarity Index (SSIM).]
	The SSIM for two random variables $X$ and $Y$ is defined in \cite{ahmed_benchmark_2016, akramullah_video_2014} as
	\begin{align}
		\mathrm{SSIM}(X,Y) = \frac{(2\mu_X\mu_Y+c_1)(2\sigma_{XY}+c_2)}{(\mu_X^2+\mu_Y^2+c_1)(\mu_X^2+\mu_Y^2+c_2)}
	\end{align}
	where
	\begin{itemize}
		\item $\mu_X, \mu_Y$ are the averages of $X$ and $Y$, respectively;
		\item $\sigma_X, \sigma_Y$ are the variances of $X$ and $Y$, respectively;
		\item $\sigma_{XY}$ is the covariance of $X$ and $Y$;
		\item $c_1 = (k_1L)^2, c_2 = (k_2L)^2$ are two variables used to stabilize the measure when $\mu_X^2+\mu_Y^2$ is close to zero \cite{akramullah_video_2014};
		\item $L$ is the the maximum pixel intensity value of an image;
		\item $k_1 = 0.01, k_2 = 0.03$ by default, given in \cite{ahmed_benchmark_2016}.
	\end{itemize}
	The SSIM is applied to the luminance value of two images to gauge structural similarity between neighboring pixels.
	For the study, we will compute $\mathrm{SSIM}(\mathrm{PDT}, \mathrm{CDT})$ for every image operation, under each homomorphic cryptosystem. Higher values of SSIM indicate higher structural similarity, and an SSIM of 1 indicates that the two images are identical\cite{ahmed_benchmark_2016}.
\end{description}

@@

	We will compute $H(\mathrm{CDT})$ for every image operation, under each homomorphic cryptosystem, and compare the effects of each image operation on the entropy of the encrypted image. Ideally, performing image operations on encrypted images should still maintain a high level of entropy.
	\item [Correlation coefficient analysis (CC).]
		Images generally have a high degree of similarity between adjacent pixels. This correlation must be hidden in the encrypted image, even after performing image operations.
		The correlation coefficient of an image can be computed between adjacent pixels either vertically, horizontal, or diagonally, and is defined in \cite{ahmed_benchmark_2016} by:
		\begin{align}
			\mathrm{CC}(X,Y) = \frac{\sigma_{X,Y}}{\sqrt{\sigma_X}\times\sqrt{\sigma_Y}}
		\end{align}
		where
		\begin{itemize}
			\item $\sigma_X, \sigma_Y$ are the variances of $X$ and $Y$, respectively;
			\item $\sigma_{XY}$ is the covariance of $X$ and $Y$.
		\end{itemize}

		For every $\mathrm{CDT}$ image, we will compute for the correlation coefficient (for vertical, horizontal and diagonal correlation) for every image operation, under each homomorphic cryptosystem.
	\item [NPCR and UACI.]
		The Number of Pixel Change Rate (NPCR) measures the number of pixels which are changed between the a plaintext and a ciphertext to quantify the amount of dispersion which occurs during encryption.

@@

		The NPCR and UACI between two images $X$ and $Y$, each containing $N$ pixels indexed from $1$ to $N$ is defined in \cite{wu_npcr_2011} as
		\begin{align}
			\mathrm{NPCR}(X,Y) &= \frac{1}{N}\sum_{i = 1}^{N}{D(X_i,Y_i)} \times 100\%\\
			\mathrm{UACI}(X,Y) &= \frac{1}{L_{\max} \times N} \sum_{i = 1}^{N}{ |L(X_i) - L(Y_i)| } \times 100\%
		\end{align}
		where
		\begin{itemize}
			\item $X_i$ and $Y_i$ are the $i$th pixels of $X$ and $Y$, respectively;
			\item $D$ is a difference function between pixels $A$ and $B$ defined by
			\begin{align}
				D(A,B) =
				\begin{cases}
					0 &  \text{if $A = B$},\\
					1 &  \text{if $A \neq B$};
				\end{cases}
			\end{align}
		\item $L_{\max}$ is the maximum intensity of a pixel;
		\item $L(X_i)$ and $L(Y_i)$ are the intensities of pixels $X_i$ and $Y_i$, respectively.
		\end{itemize}
		We will calculate $\mathrm{NPCR}(\mathrm{PDT},\mathrm{CDT})$ and $\mathrm{UACI}(\mathrm{PDT},\mathrm{CDT})$  for every image operation, under each homomorphic cryptosystem. A high NPCR and UACI are desired to ensure high dispersion and security against differential attacks \cite{ahmed_benchmark_2016}. Critical values for NPCR and UACI for given image sizes and bit depths are given in  \cite{wu_npcr_2011}.
\end{description}
